Logsums

### 2019-09-24 03_logsums.Rmd
Move spatial weights calculation to estimation file
It makes more sense to think about the spatial weights as a function of the estimation rather than a function of the logsums. But this requires that we export a couple of additional datasets.

```{r pop_weighted_centroids}
pop_weighted_centroids <- tracts %>% tbl_df() %>%
  dplyr::select(geoid) %>%
  left_join(
    read_csv("https://www2.census.gov/geo/docs/reference/cenpop2010/tract/CenPop2010_Mean_TR36.txt") %>%
      transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE), LATITUDE, LONGITUDE)
  ) %>%
  # convert to sf and project into the feet-based projection used in the
  # parks dataset.
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(3628)
```

@@

```{r W}
# determine which tracts are neighbors of each other. Need to be less than
# 1.8 miles away from the centroids
tracts.dnn <- dnearneigh(as(pop_weighted_centroids, "Spatial"), 0, 1.8 * 5280)
# calculate the inverse distance to use as a weight on the neighbor connection
dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
dists.inv <- lapply(dists, function(x) 1 / x)
# get the spatial weights matrix and its trace to use in any impact analyses
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
print(W, zero.policy = TRUE)
```

@@

write_rds(distances, "data/distances.rds")
write_rds(W, "data/W.rds")
```

>>>>

```{r pop_weighted_centroids}
pop_weighted_centroids <- tracts %>% tbl_df() %>%
  dplyr::select(geoid) %>%
  left_join(
    read_csv("https://www2.census.gov/geo/docs/reference/cenpop2010/tract/CenPop2010_Mean_TR36.txt") %>%
      transmute(geoid = str_c(STATEFP, COUNTYFP, TRACTCE), LATITUDE, LONGITUDE)
  ) %>%
  # convert to sf and project into the feet-based projection used in the
  # parks dataset.
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(3628) %>%
  write_rds("data/pop_weighted_centroids.rds")

```

@@

```{r W}
# determine which tracts are neighbors of each other. Need to be less than
# 1.8 miles away from the centroids
tracts.dnn <- dnearneigh(as(pop_weighted_centroids, "Spatial"), 0, 1.8 * 5280)
# calculate the inverse distance to use as a weight on the neighbor connection
tract_dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
write_rds(tract_dists, "data/tract_distances.rds")
```

@@

write_rds(distances, "data/distances.rds")
```
